On hyperparameter tuning through Lipschitz global optimization

### 2023-09-01 2023/ITMO paper/elsarticle-template-num.tex
translate one sectence in Rissuan

%% Русский язык - закомментировать в финальной версии
\usepackage[russian]{babel}

@@

The simplest way to find the global optimum is the exhaustive search method (поиска по равномерной \cite{Bao2006} или случайной \cite{Bergstra2012} сетке). By selecting the number of analyzed variants for each of the hyperparameters, searching all the resulting combinations and choosing the best of them in a given metric, we obtain an estimate of the optimum with a certain accuracy \cite{Nevendra2022}. The exhaustive search method is easy to implement, it has perfect parallelism, but it has a significant drawback (an exponential growth of the number of grid nodes as the number of hyperparameters increases). Thus, exhaustive search can be used as a method for solving HPO problems only in "simple" problems where both the number of hyperparameters (one or two) and the time for solving the initial problem with each selected combination of hyperparameters are small.

>>>>

%% Русский язык - закомментировать в финальной версии
%\usepackage[russian]{babel}

@@

The simplest way to find the global optimum is the exhaustive search method (search on the uniform \cite{Bao2006} or random \cite{Bergstra2012} grid). 
By selecting the number of analyzed variants for each of the hyperparameters, searching all the resulting combinations and choosing the best of them in a given metric, we obtain an estimate of the optimum with a certain accuracy \cite{Nevendra2022}. The exhaustive search method is easy to implement, it has perfect parallelism, but it has a significant drawback (an exponential growth of the number of grid nodes as the number of hyperparameters increases). Thus, exhaustive search can be used as a method for solving HPO problems only in "simple" problems where both the number of hyperparameters (one or two) and the time for solving the initial problem with each selected combination of hyperparameters are small.
